\documentclass{article}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[utf8]{inputenc}

\usepackage{amsmath, amssymb}
\usepackage{amsthm}
\usepackage{enumitem}
\newtheoremstyle{breakstyle}
	{5pt}
	{10pt}
	{\normalfont}
	{0pt}
	{\bfseries}
	{}
	{\newline}
	{}
\theoremstyle{breakstyle}
\newtheorem{exercise}{Exercise}[section]
\title{Chapter 1 - Roots of Commutative Algebra}
\setlist[enumerate,1]{
    label=(\roman*), 
    topsep=0pt, 
    partopsep=0pt, 
    parsep=0pt,
    leftmargin=*
}

\author{Flandre}
\date{15 Jan 2026}

\begin{document}
\maketitle

\setcounter{section}{1}
\begin{exercise}
	\leavevmode \vspace{-\baselineskip}
	\begin{enumerate}
		\item \emph{(1)}$\Rightarrow$\emph{(2)}:
			Suppose there exist a chain $\{N_{k}\}_{k=1}^{\infty}$ which is a none stopping ascending chain, we denote 
			$$
			\bigcup_{k =1} ^{\infty}N_{k}=N
			$$ 
			and by \emph{(1)}, $N$ is a finitely generately submodule of $M$.
			Suppose $\left\{ n_1,n_2,\ldots,n_{r} \right\} $ is the generator of $N$, and each $n_{k}$ is in one of the submodule ${N_{i}}$.
			Now by the infinte ascending chain, there exist $N_{j}$ such that $N_{j}\supseteq {n_1,\ldots,n_{r}}$.
			And we pick out
			$$
			n \in N_{j+1}\backslash N_{j}
			$$
			and notice $n \in N$, contradictory!
		\item \emph{(2)}$\Rightarrow$\emph{(3)}:
			Denote such set of submodules by $\Sigma$.

			First we pick out $N_1\in \Sigma$. If $N_1$ is maximal, \emph{(2)} holds.
			Otherwise $\exists N_2\in \Sigma,N_2\supseteq N_1$. If $N_2$ is maximal, again  \emph{(3)} holds, otherwise $\exists N_3\in \Sigma,N_3\supseteq N_2$.
			Under such method, we can derive a chain $N_1,N_2,N_3,\ldots$ which satisfy the A.C.C., therefore by \emph{(2)} it must terminate.
		\item \emph{(3)}$\Rightarrow$\emph{(1)}:
			For any submodule $N$, let $\Sigma$ be the set of all finitely generated submodules of $N$.
			Since  $\left\{ 0 \right\} \subseteq\Sigma$, $\Sigma$ is nonempty.

			Now we pick out $N_0$ to be the maximal element of $\Sigma$.
			If $N=N_0$, \emph{(1)} holds.
			Otherwise let $n\in N\backslash N_0$.
			Notice the base of $N_0$, together with $\left\{ n \right\} $, generate a finitely generated submodule of $N$, which contradict with the maximality of $N_0$.
		\item \emph{(2)}$\Rightarrow$ \emph{(4)}:
			Let $\left\{ N_{k} \right\} _{k=1}^{\infty}$ be a sequence of submodules, whose $k $-th term is generated by $\left\{ f_1,f_2,\ldots,f_{k} \right\} $.
			With out loss of generality we assume $N_{k}\subsetneq N_{k+1},\forall k$.
			By \emph{(2)}, the chain $\left\{ N_{k} \right\} $ must termiante, therefore the condition in \emph{(4)} holds.
		\item \emph{(4)}$\Rightarrow$\emph{(2)}:
			Suppose there is a chain of submodules $\left\{ N_{k} \right\} $, we'll prove it'll termiante somewhere.

			For each $k\in \mathbb{N}$, pick out $f_{k}\in N_{k}\backslash N_{k-1}$.
			Now by \emph{(4)},
			$$
			\exists m\in \mathbb{Z}^{+},s.t.\ \forall n>m,\ \exists a\in \mathbb{R},s.t.\ f_{n}=\sum_{k=1}^{m} a_{k}f_{k},\ \mathrm{for}\ a_{k}\in R
			$$ 
			Therefore the ascending chain $\left\{ N_{k} \right\} $ termiante!
	\end{enumerate}
	\qed
\end{exercise}

\begin{exercise}
	Suppose by contradictory that the proposition is wrong, and we denote the set of ideal having infinte amount of minimal prime ideals by $\Sigma$.

	Since $N$ is Noetherian, we may pick out a maximal ideal $I\in \Sigma$.
	If $I$ is prime, $I$ is the unique minimal prime ideal over itself, contradictory.
	On the otherhand, if $I$ is not prime. Then
	$$
	\exists a,b\in R,s.t.\ ab\in I,a,b \not\in I
	$$ 
	Consider $J_1=(I,a)$ and $J_2=(I,b)$.
	For any minimal prime ideal $J\supseteq I$, since it's prime, $ab\in I\subseteq J$ must induce $a\in J$ or $b\in J$, i.e. $J$ is a minimal prime over $J_1$ or $J_2$.

	Because there're infinte many amount of $J$, we see there'll be at least one of the ideal among $J_1,J_2$, which has infinte amount of minimal prime ideals, contradicting the maximality of $I$.
	\qed
\end{exercise}

\begin{exercise}
	\leavevmode \vspace{-\baselineskip}
	\begin{enumerate}
		\item $(\Rightarrow)$:
			When $M$ is Noetherian, $M'$ must be Noetherian.
			By the \emph{Lattice Isomorphism Theorem}, there is a bijection
			$$
			\mathrm{submodules\ of\ }M\mathrm{\ that\ contains\ M'}\longleftrightarrow\mathrm{submodules\ of\ }M / M'
			$$ 
			Now for any submodules of $M / M'$ let $N$ be the correspond submodule of $M$ which contians $M'$.
			Consider
			$$
			(m_1,\ldots,m_{n})
			$$
			to be the generators of $n$.
			Now for $\overline{N}=N / M'$, its generator will be
			$$
			(\overline{m_1},\ldots,\overline{m_{n}})
			$$
			Which is finite.
		\item $(\Leftarrow)$:
			% When $M'$ and $M / M'$ are both Noetherian, consider the map
			% $$
			% \varphi:M\longrightarrow M / M'
			% $$
			% $$
			% m\longmapsto \overline{m}
			% $$
			% Its kernel is $M'$ and its image is $M / M'$.
			% Suppose $M'$ is generated by $\left\{ k_1,\ldots,k_{s} \right\} $ while $M / M'$ is generated by $\left\{  \right\} $
			When $M'$ and $M / M'$ are both Noetherian, for any submodule $N\subseteq M$, we'll prove $N$ is Noetherian.
			\begin{enumerate}
				\item When $N\subseteq M'$, $N$ is Noetherian and it's done.
				\item When $M'\subseteq N$, by \emph{Lattice Isomorphism Theorem} $N$ correspond to $N / M'$, which is a submodule of $M / M'$.
					Suppose $N / M'$ is generated by
					$$
					(\overline{m_1},\ldots,\overline{m_{n}})
					$$
					Of each generators above, we consider its preimage, which is the coset $m_1+M'$.
					Since $M'$ is finitely generated, those cosets can be finitely expressed, and $N$ is finitely generated.
				\item When $M'\backslash N,N\backslash M$ are both nonempty, consider $N\backslash M'$ quotient by $N\cap M'$, similar the the case \emph{(b)}.
			\end{enumerate}
	\end{enumerate}
	\qed
\end{exercise}

\begin{exercise}
	
\end{exercise}

\end{document}
